Architectures for workflow integration in science gateways

### 2016-04-12 paper.tex
Wrote section 4.5

\todo{Introduce the notion of architectural diagram with an abstract figure.}

@@

= Evaluation
+ Scale-up and load balancing
+ Multi-language
- Needs a complete framework (the pool). Most likely third-party software as it's a lot of work to implement.

@@

\begin{table*}
\centering
\begin{tabular}{rcccccc}
\textbf{Metric}                      & \textbf{Tight}
                                     & \textbf{Service}
                                     & \textbf{Sub-task}
                                     & \textbf{Pool}
                                     & \textbf{Nested}
                                     & \textbf{Import} \\
\multicolumn{7}{c}{\cellcolor[HTML]{EEEEEE}\textbf{Integration}}\\
Science gateway -- \texttt{I$_1$}    & \multirow{2}{*}{3}
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99FF99}0  
                                     & \cellcolor[HTML]{99FF99}2
                                     & \cellcolor[HTML]{99FF99}2
                                     & \cellcolor[HTML]{99AA99}3 \\
Workflow engine -- \texttt{I$_2$}    &
                                     & \cellcolor[HTML]{99FF99}3 
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99AA99}2
                                     & \cellcolor[HTML]{99AA99}2
                                     & \cellcolor[HTML]{99FF99}1 \\
Infrastructure -- \texttt{I$_3$}   & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99FF99}0 \\
Other -- \texttt{I$_4$}              & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99AA99}2
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99FF99}0 \\
\textbf{Total}                       & \cellcolor[HTML]{99FF99}\textbf{3}
                                     & \cellcolor[HTML]{99FF99}\textbf{4}
                                     & \cellcolor[HTML]{99FF99}\textbf{2}
                                     & \cellcolor[HTML]{99AA99}\textbf{4}
                                     & \cellcolor[HTML]{99AA99}\textbf{4}
                                     & \cellcolor[HTML]{99AA99}\textbf{4} \\

@@

                                     & \cellcolor[HTML]{99EE99}\textbf{6}

@@

@@

\caption{Architecture evaluation. Lower values (brighter colors) indicate better performance.}

>>>>

\todo{Introduce the notion of architectural diagram with an abstract figure. Mention arrows, boxes, box with dotted lines, red color.}

@@

\paragraph{Integration} Integrating workflow engines through the pool
model requires interaction \texttt{d} in the science gateway
(\texttt{I$_1$=1}), interactions \texttt{b} and \texttt{c$_2$} in the
workflow engine (\texttt{I$_2$=2}), the development of the workflow
pool, agent and interaction \texttt{f} between them
(\texttt{I$_4$=3}).

\paragraph{Robustness} The science gateway, workflow pool, agent and
infrastructure are involved in a workflow execution
(\texttt{R$_1$=4}), and these components are connected through 4
interactions (\texttt{R$_2$=4}). Accessing debugging information is
not likely to be an issue since the workflow pool could implement
specific functions for that (\texttt{R$_3$=0}).

\paragraph{Modularity} Adding a new engine type requires to wrap the
engine in the agent and to update interactions \texttt{b} and
\texttt{c$_2$} (\texttt{M$_1$=3}). Updating the version of an engine
is transparent (\texttt{M$_2$=0}), and integrating a new
infrastructure requires updates in interactions \texttt{b},
\texttt{c$_1$} and \texttt{c$_2$} (\texttt{M$_3$=3}). Integrating a
new workflow is done through interaction \texttt{a} only
(\texttt{M$_4$=1}) and meta-workflows are not available by default
(\texttt{M$_5$=1}).

\paragraph{Scalability} New engine instances only require new agents,
which is easily automated (\texttt{S$_1$=0}) and by design very
suitable for elastic computing (\texttt{S$_2$=0}). For instance,
auto-scaling rules can be implemented to start new agents when the
workload in the science gateway exceeds a certain threshold \todo{ref
  needed}. Distributed engines are not available by default
(\texttt{S$_3$=1}) and task scheduling is as complex as in any other
architecture (\texttt{S$_4$=0}).

@@

\begin{table*}
\centering
\begin{tabular}{rcccccc}
\textbf{Metric}                      & \textbf{Tight}
                                     & \textbf{Service}
                                     & \textbf{Sub-task}
                                     & \textbf{Pool}
                                     & \textbf{Nested}
                                     & \textbf{Import} \\
\multicolumn{7}{c}{\cellcolor[HTML]{EEEEEE}\textbf{Integration}}\\
Science gateway -- \texttt{I$_1$}    & \multirow{2}{*}{3}
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99FF99}0  
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99FF99}2
                                     & \cellcolor[HTML]{99AA99}3 \\
Workflow engine -- \texttt{I$_2$}    &
                                     & \cellcolor[HTML]{99FF99}3 
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99AA99}2
                                     & \cellcolor[HTML]{99AA99}2
                                     & \cellcolor[HTML]{99FF99}1 \\
Infrastructure -- \texttt{I$_3$}   & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}1
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99FF99}0 \\
Other -- \texttt{I$_4$}              & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99FF99}0
                                     & \cellcolor[HTML]{99AA99}3
                                     & \cellcolor[HTML]{99AA99}0
                                     & \cellcolor[HTML]{99FF99}0 \\
\textbf{Total}                       & \cellcolor[HTML]{99FF99}\textbf{3}
                                     & \cellcolor[HTML]{99FF99}\textbf{4}
                                     & \cellcolor[HTML]{99FF99}\textbf{2}
                                     & \cellcolor[HTML]{99AA99}\textbf{6}
                                     & \cellcolor[HTML]{99AA99}\textbf{4}
                                     & \cellcolor[HTML]{99AA99}\textbf{4} \\

@@

                                     & \cellcolor[HTML]{99EE99}\textbf{8}

@@

                                     & \cellcolor[HTML]{99CC99}\textbf{23}

@@

\caption{Architecture evaluation. Lower values (brighter colors) indicate better performance. \todo{update colors and find a more relevant way to compute a grand total without favoring criteria that have more metrics than the others (e.g. normalize each criterion between 0 and 1).}}
